Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A guide for Vietnamese and International Students

### 2023-06-12 phd-cs-us.tex
updates

\subsection{Letters of Recommendation (LORs)}

@@

Many students have letters written by the applicants themselves and signed by their professors. These have little
values (we can easily recognize them) and will consider them weakness.
Similarly, many professors write very generic letters for students (a common example is that the students didn't do any
research or make any impression for the professor to write about). These letters are also not useful and considered weak.

@@

\subsection{How do I address a professor?}
If you don't know that professor (e.g., first email contact), then use \textbf{Prof. Lastname} or \textbf{Dr. Lastname}. I've seen many international students write \textbf{Prof.} or \textbf{Dr.} \textbf{Firstname Lastname}.  Writing like that makes it like you copy and paste the names, so no need to do so,  just Prof. or Dr. Lastname.

>>>>

\subsection{Letter of Recommendation (LOR)}\label{sec:lor}

@@

\begin{wrapfigure}{r}{0.45\textwidth}
    \vspace{-0.3in}
      \begin{center}
        \includegraphics[width=0.45\textwidth]{c6.png}
      \end{center}
    \vspace{-0.4in}
    \end{wrapfigure}
Many students have letters written by the applicants themselves and signed by their professors. These have little
values (we can easily recognize them) and will consider them weakness.
Similarly, many professors write very generic letters for students (a common example is that the students didn't do any
research or make any impression for the professor to write about). These letters are also not useful and considered weak.

@@

\subsection{How do I address a professor?}

\begin{wrapfigure}{l}{0.47\textwidth}
    \vspace{-0.3in}
      \begin{center}
        \includegraphics[width=0.47\textwidth]{c5.png}
      \end{center}
    \vspace{-0.6in}
    \end{wrapfigure}
If you don't know that professor (e.g., first email contact), then use \textbf{Prof. Lastname} or \textbf{Dr. Lastname}. I've seen many international students write \textbf{Prof.} or \textbf{Dr.} \textbf{Firstname Lastname}.  Writing like that makes it like you copy and paste the names, so no need to do so,  just Prof. or Dr. Lastname.
